### 2022-01-09 paper/issta22/intro.tex
intro

On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. They approach evaluating
robustness of the model on adversarial sets~\cite{}, fairness~\cite{},
logical consistancy~\cite{}, explanations~\cite{}, diagnostic
datasets~\cite{}, and interactive error analysis. In addition,
inspired by the behavioral testing of software engineering research,
Marco \etal proposed a tool for comprehensive behavioral
testing of NLP models~\cite{marcoACL2020checklist}

%% Machine learning testing poses challenges that arise
%% from the fundamentally different nature and construction
%% of machine learning systems, compared to traditional (relatively more deterministic and less statistically-orientated)
%% software systems.

%% \Nlp testing is crucial part for developing a reliable \Nlp
%% applications. For developing \Nlp applications, testing is mainly used
%% to check the ML model's performance on \ho set with respect to the
%% accuracy of the model. The \ho data refers to a portion of dataset
%% that is held out of the datasets used for training \ml
%% models. Generally, the \ho set is extracted via Train-Validation-Test
%% split.

%% One of the primary goals of training NLP models is
%% generalization. Since testing “in the wild” is expensive and does not
%% allow for fast iterations, the standard paradigm for evaluation is
%% using trainvalidation-test splits to estimate the accuracy of the
%% model, including the use of leader boards to track progress on a task
%% (Rajpurkar et al., 2016).

%% While performance on held-out data is a
%% useful indicator, held-out datasets are often not comprehensive, and
%% contain the same biases as the training data (Rajpurkar et al., 2018),
%% such that real-world performance may be overestimated (Patel et al.,
%% 2008; Recht et al., 2019). Further, by summarizing the performance as
%% a single aggregate statistic, it becomes difficult to figure out where
%% the model is failing, and how to fix it (Wu et al., 2019).

>>>>

On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. First, multiple diagnostic
datasets for evaluating NLP model were introduced for obtaning
generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
that, model is evaluated on different aspects such as robustness of
the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.

In this paper, we present \Model, an automated NLP model evaluation
method for comprehensive behavioral testing of NLP models on \sa
task. For each behavior of linguistic capability, \Model does not rely
on the manual input generation. Instead, it establishes input
requirement for evaluating a linguistic capability and finds suitable
inputs that meet the requirement from existing public dataset.
Therefore, \Model increases input diversity and generality. Further,
\Model applies the fuzzing testing principle to generate inputs by
mutating the selected inputs as seed inputs. Fuzzer in \Model first
expands seed input grammar structures and determines its available
\pos to maintain structural naturalness. After that, to hold
contextual naturalness of the mutated inputs, the fuzzer completes the
expanded new structures via data-driven context-aware word
suggestion. Additionally, sentiment-independent words in the inputs
are replaced with rule-based word suggestion.

We demonstrate its generality and utility as a NLP model evaluation
tool by evaluating well-known \sa models: \Bert~\cite{devlin2019bert},
\Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
We show that
